%-------------------------------------------
% Yesrab Ali — Resume
% Uses: cvhari.cls
% Compile with pdflatex on Overleaf (upload both files)
%-------------------------------------------

\documentclass{cvhari}

\begin{document}

%----------HEADER----------
\begin{center}
  {\Huge\bfseries\scshape\color{primary} Yesrab Ali} \\[5pt]
  \small
  \faPhone~7013809402 \quad $|$ \quad
  \faEnvelope~\href{mailto:yesrab.ali111@gmail.com}{\underline{yesrab.ali111@gmail.com}} \quad $|$ \quad
  \faGithub~\href{https://github.com/yesrab}{\underline{github.com/yesrab}} \quad $|$ \quad
  \faLinkedin~\href{https://linkedin.com/in/yesrabali/}{\underline{www.linkedin.com/in/yesrabali}}
\end{center}

%----------SUMMARY----------
\vspace{2pt}
{\small
Frontend Developer with expertise in Next.js, React, TypeScript, and Node.js, focused on building scalable, high-performance web applications. Experienced in migrating legacy systems, developing data visualization features, and delivering seamless user experiences. Passionate about crafting clean, modular code and driving measurable improvements in system reliability and usability.
}
\vspace{4pt}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Seamless Distribution Systems}{01/2025 -- Present}
      {Software Development Engineer (SDE)}{Remote}
      \resumeItemListStart
        \resumeItem{Enhanced MTN South Africa reporting capabilities by developing new data visualization features, creating dynamic charts and graphs to deliver deeper business insights.}
        \resumeItem{Led the full transformation for Grameenphone (Bangladesh), successfully migrating legacy system workflows to seamless IDM and ERS platforms, streamlining operations and improving system reliability end-to-end.}
        \resumeItem{Accelerated a 6-month legacy React app migration plan to a 1-month delivery by converting outdated UI component libraries to modern React concepts and components.}
      \resumeItemListEnd

   \resumeSubheading
      {Seamless Distribution Systems}{07/2024 -- 01/2025}
      {React Developer Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Built an Inventory Dashboard revamp, improving usability and providing real-time inventory visibility, empowering stakeholders with timely data.}
        \resumeItem{Contributed to front-end development for IDM Localization, enabling seamless adaptation of interfaces for multiple regions and enhancing global usability.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{X Management System} $|$ \emph{Next.js 16, NestJS 11, PostgreSQL, Prisma ORM, TypeScript}}{2026 -- Present}
          \resumeItemListStart
            \resumeItem{Building a multi-tenant education management platform for schools, colleges, and universities as an Nx monorepo with a Next.js 16 App Router frontend and NestJS 11 backend.}
            \resumeItem{Implemented a granular RBAC permission system (Organization $\to$ Policy $\to$ FeatureCollection $\to$ ModuleFeature) supporting org-scoped roles with route, component, and API-level access control.}
            \resumeItem{Integrated secure authentication using argon2id password hashing and JWT sessions via jose; containerized with Docker for dev and production environments.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{MusiCart} -- Audio Equipment E-Commerce $|$ \emph{React, Node.js, Express, MongoDB} $|$ \href{https://music-cart-yesrab.vercel.app/}{\underline{Live Demo}}}{2024}
          \resumeItemListStart
            \resumeItem{Designed an e-commerce platform for headphones with intuitive search, multi-parameter filtering (type, company, color, price range), and sorting by price and alphabetical order.}
            \resumeItem{Built a seamless cart and checkout flow with secure address input, payment selection, and an invoices page for order tracking.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Job Finder} -- Recruitment Portal $|$ \emph{React, Node.js, Express, MongoDB, JWT} $|$ \href{https://job-finder-yesrab.vercel.app/}{\underline{Live Demo}}}{2024}
          \resumeItemListStart
            \resumeItem{Developed a MERN stack application enabling recruiters to post jobs and candidates to browse, filter, and share listings by title and skills; fully responsive across desktop and mobile.}
            \resumeItem{Leveraged React Router DOM data loader API and React Suspense to optimize data fetching and component loading performance, with JWT-based authentication.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Pro Manage} -- Group Task Management App $|$ \emph{React, Node.js, MongoDB} $|$ \href{https://pro-manage-yesrab.vercel.app/}{\underline{Live Demo}}}{2023}
          \resumeItemListStart
            \resumeItem{Built a fully functional task management app with 4-section project categorization, subtask tracking, and a color-coded timeline system for visual project progress.}
            \resumeItem{Implemented a robust sharing mechanism for seamless collaboration among multiple stakeholders.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vasireddy Venkatadri Institute of Technology}{Guntur, India}
      {Bachelor of Technology in Mechanical Engineering $|$ GPA: 7.61}{2019 -- 2023}
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeItem{\textbf{AWS Academy Cloud Foundations} -- AWS Academy}
    \resumeItem{\textbf{Software Testing} -- NPTEL}
    \resumeItem{\textbf{Fundamentals of Digital Marketing} -- Google Digital Garage \hfill \textit{\small Cert ID: UAU J5X E9F}}
    \resumeItem{\textbf{Teamcenter} -- APSSDC \hfill \textit{\small Cert No: OFF-08-1211}}
    \resumeItem{\textbf{Basic Robotics} -- APSSDC \hfill \textit{\small Cert No: OFF-08-1060}}
  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Publications}
  \resumeSubHeadingListStart
    \resumeItem{\textbf{Autonomous Fire Extinguisher} -- \textit{International Journal For Innovative Engineering and Management Research}, Volume 12 Issue 4, April 2023}
     \href{https://ijiemr.org/downloads/paper/Volume-12/autonomous-fire-extinguisher}{\underline{Read here}}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages \& Frameworks:} JavaScript (ES6+), TypeScript, React.js, Next.js, Node.js, NestJS, Express.js \\[3pt]
     \textbf{Frontend Tools \& Libraries:} Tailwind CSS v4, shadcn/ui, Material UI, TanStack React Form, Zod \\[3pt]
     \textbf{Backend \& Database:} PostgreSQL, MongoDB, Prisma ORM \\[3pt]
     \textbf{DevOps \& Tools:} Docker, Git, pnpm, Nx Monorepo, JWT, Linux \\[3pt]
     \textbf{Design:} Adobe Photoshop \\[3pt]
     \textbf{Practices:} Agile, Responsive Design, RBAC, Micro-frontend Architecture \\[3pt]
     \textbf{Languages:} English, Hindi, Telugu
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
